### 2016-04-12 Chapters/chap3/Manuscript-FINAL.tex
Improve fig, revision
Gonna give it to the committee

\chapter{Primary Mode and Its Relation to Reaction Dynamics}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}

@@

One of the most important and fundamental processes in chemical  dynamics is
that of energy and charge transfer between molecular species.  The mechanism
itself is highly quantum mechanical in nature and involves strong coupling between nuclear and
electronic degrees of freedom.  The seminal model for the calculation of the transfer rate for this process
was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
\begin{equation}
k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
\end{equation}
which relates the Fermi golden-rule transition rate, $k_{Marcus}$
to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$.
One of the most striking predictions of this theory is that as the free energy difference between the final and initial state increases, the transition rate reaches its maximum,
and further increases in the energy off-set leads to slower transition rates.
This ``inverted regime''  was confirmed by Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
nearly 30 yrs later.

Numerous improvements to the Marcus model have been presented over the years and
a detailed exploration of each is well beyond the scope of this work.
Aside from the electronic coupling, $V_{ab}$,  the other terms in the expression of rate constant arise from
a semi-classical approximation to the overlap between the initial vibrational states of the donor and the
the final  states of the acceptor state. It suffices to say that most of the
efforts focus upon incorporating more molecular-level detail into the couplings and vibrational modes
used in computing these terms.

A number of years ago,  we developed a time-convolutionless  master equation approach (TCLME) for computing
state-to-state rate in which the coupling between  states depends upon the
nuclear coordinates \cite{pereverzev2006time}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
the Marcus rate equation in the semi-classical limit.  The model itself is parameterized by the
vibrational normal mode frequencies, the electronic energies, and energy derivatives
at a reference configuration obtained from {\em ab initio} quantum  chemistry computations.
The approach has been intensively used and testified by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
 \cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise}.
Central to our work here is the use of a mode-projection scheme
 % which is similar to the Page-rank algorithm used by internet search engines such as
 % Google and Netflix\cite{brin1998anatomy, page2004method},
 which parses out a
reduced set of nuclear motions primarily coupled to the quantum transition.
We refer to the modes identified early in the iterative process as the ``primary Lanczos modes'' or PLMs.

Using the TCLME approach,  we recently investigated
triplet-triplet excitation energy transfer between a naphthalene donor and a
benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{yang2014intramolecular}
\begin{figure}
%\includegraphics[width=\columnwidth]{Chapters/chap3/D-B-A-Numbered.pdf}
\includegraphics[width=\columnwidth]{Chapters/chap3/molecule1.pdf}
\caption{Molecular structure of naphthalene donor and a
benzaldehyde acceptor linked by various bridging units. }\label{struct}
\end{figure}
Such systems were the basis of a  classic series of experiments by
Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
which verified the existence of the Marcus inverted regime.
In Ref. \cite{yang2014intramolecular} we showed that both
the autocorrelation function of the electronic coupling operators
and the total transfer rate constant calculated using TCLME approach with only PLMs provide an
excellent approximation to the exact correlation functions and rate
constants computed using all normal modes, as well as to the experimental
and recent theoretical values for the transfer rates \cite{subotnik2010predicting}.

In this paper we analyze the symmetry of PLMs in model donor-bridge-acceptor systems as projected onto the local
 vibrational modes of the  donor (benzaldehyde)    and  acceptor (naphthalene) moieties.    By constructing the local modes
from the dominant normal modes in the projection,  one can deduce a relation between the PLMs,
fragment modes,  and normal modes for the entire molecule.
The structure of this paper is as follows.
We begin by reviewing the TCLME approach and how one generates the PLMs.  We then
discuss the symmetry  of PLMs and their relation to a linear coordinate linking the
initial/donor geometry to the final/acceptor geometry of the molecule.
%---NEED CONCLUDING STATEMENT----

\section{Theoretical Model}

@@

\subsection{Hamiltonian and Parameterization}

We start with the  generic form for the diabatic Hamiltonian, describing two electronic states coupled with $N$ normal modes:
\begin{eqnarray}
H_{dia}=\left(\begin{array}{cc}
\epsilon_{1} & V_{12}\\
V_{21} & \epsilon_{2}
\end{array}\right)
+\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
\nonumber \\
\end{eqnarray}
Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
reference geometry--typically that of the donor or acceptor state. $V_{ij}$ is the diabatic coupling between them.  The second term represents the
linear coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
normal coordinates $\mathbf q$.   The diagonal terms
give the diabatic displacement forces between the reference geometry and the two states.
The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.

If we choose one of the states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish. We further assume Condon approximation to neglect $\mathbf g_{12}$ and $\mathbf g_{21}$. Now the Hamiltonian is simplified to
\begin{eqnarray}
H_{dia}=\left(\begin{array}{cc}
\epsilon_{1} & V_{12}\\
V_{21} & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
0 & 0\\
0 & 1
\end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
\end{eqnarray}
\label{eq:diaHam}
where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.

To calculate transition rate, we transform to adiabatic representation. It is done via Edmiston-Ruendenberg (ER) localization \cite{subotnik2010predicting} implemented in Q-Chem and the electronic Hamiltonians
on adiabatic and diabatic basis are related by the mixing angle $\theta$.
\begin{equation}
H_{dia,e}=\left(\begin{array}{cc}
\cos\theta & -\sin\theta\\
\sin\theta & \cos\theta
\end{array}\right)\left(\begin{array}{cc}
\epsilon_{1}  & 0 \\
0  & \epsilon_{2}
\end{array}\right)\left(\begin{array}{cc}
\cos\theta & \sin\theta\\
-\sin\theta & \cos\theta
\end{array}\right).
\end{equation}
The diabatic coupling is then given by
\begin{eqnarray}
V_{12}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
\end{eqnarray}
The full adiabatic Hamiltonian reads:
\begin{eqnarray}
H&=&U^{T}H_{dia}U\nonumber  \\
&=&\left(\begin{array}{cc}
E_{1}  & 0 \\
0 & E_{2}
\end{array}\right)+\left(\begin{array}{cc}
\sin^{2}\theta & \frac{1}{2}\sin2\theta\\
\frac{1}{2}\sin2\theta & \cos^{2}\theta
\end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
&+& H_{osc}.\label{eq:locaiHam2}
\end{eqnarray}
where the electronic part is in the adiabatic basis with eigenenergies of $E_1$ and $E_2$ at certain reference geometry. The nuclear normal modes are described by $H_{osc}$ whereas $\theta$ is the mixing angle between two states.
%to describe the coupling between two electronic states, $|1\rangle$ and $|2\rangle$  by a set of nuclear vibrational motionsdescribed by $H_{osc}$.  The angle $\theta$ gives the mixing angle between diabatic states and $E_1$ and $E_{2}$ are electronic energies computed at the same reference configuration.

To parametrize our Hamiltonian, we assume the diabatic
are a good approximation to the actual adiabatic potentials.
This allows us to
use the gradients of the adiabatic potentials to approximate the diabatic potentials.
This approximation is  valid when the adiabatic (and diabatic) energy minima
are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
states is small.
Thus, all parameters in Eq.~\ref{eq:locaiHam2}  can be  obtained from
standard  quantum chemical computations.
As in our previous work, we use the Q-Chem 4.0 package  to obtain the vertical energies
 from single point CI(S) calculations with 6-31G** basis set at a given
reference geometry.   We then project the energy gradients onto the vibrational normal
coordinates

Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam2} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}. The derivation is lengthy so we present it briefly.

\subsection{Transition Rate and Autocorrelation}
We start from a more general Hamiltonian:
\begin{eqnarray}
H=\left(\begin{array}{cc}
\epsilon_{1} & 0\\
0 & \epsilon_{2}
\end{array}\right)+\left(\begin{array}{cc}
{\mathbf g}_{11}&{\mathbf g}_{12} \\
{\mathbf g}_{21} &{\mathbf g}_{22}
\end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}
\nonumber \\
% \label{ham1}
\end{eqnarray}
then perform a polaron transform
using the unitary transformation \cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
\begin{eqnarray}
U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
n|(a^{\dagger}_i-a_i)}
 \nonumber \\
&=&
\sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
% \label{unitary}
\end{eqnarray}
under which the transformed Hamiltonian is written in terms of the
diagonal elements
\begin{eqnarray} \tilde H_0=U^{-1}H_0U
=\sum_n\tilde\epsilon_n |n\rangle \langle
n|+\sum_i\omega_ia^{\dagger}_ia_i,
 \end{eqnarray}
with  the renormalized electronic energies,
\begin{eqnarray}
\tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
\end{eqnarray}
and off-diagonal terms,
\begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
% \label{opm}
\end{eqnarray}
% In the transformed (or dressed) picture the electronic transition from state
% $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% normal phonon modes.  Transforming to the interaction representation
% and performing a trace over the phonons gives the spectral density in
% terms of the autocorrelation of the electron/phonon coupling
% operators.
% \begin{eqnarray}
% S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% \end{eqnarray}
% where
% $$
%C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
After lengthy derivation we get the autocorrelation function in the Heisenberg representation
$$
C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
$$
where $\langle \cdots \rangle$ denotes a thermal average over the
vibrational degrees of freedom.
% The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% Ref.~\citenum{pereverzev2006time}.
Using this approach , the golden-rule rates are given by
\begin{eqnarray}
k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
% \label{gr-expression}
\end{eqnarray}
In a practical sense, we take $\tau$ to be some finite time at which the
autocorrelation function $C(t)$
has relaxed to zero.

Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
In our previous work we showed that both $C(t)$
and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
excellent agreement with the exact quantities computed using  the full set of
normal modes, as well as the experimental rates,
when parameterized using accurate quantum chemical data \cite{yang2014intramolecular}.

% Diagonalizing $H$ at a given nuclear configuration  provides the adiabatic potentials for our system, which can be used to approximate the diabatic potentials.

% The linear coupling parameter $ {\mathbf g}_{22}$ defines
% a force
% along a vector connecting the
% the initial and final equilibrium geometries of the molecule.
% This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
% using the ER localization
% scheme to approximate the donor and acceptor states.
% By analyzing this force we can gain the insight into the dynamics of the transition as well as
% open an avenue for developing improved approximations for transition rates.
% In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
% out a series of nuclear displacements that are most important for
% the transition.   We refer to the highest-ranked mode identified by the algorithm
% as the ``primary Lanczos mode'' (PLM).

% \subsection{Computing spectral densities and transition rates}

% Once a suitable set of parameters and vibrational modes  have been determined,

\subsection{Constructing Primary Lanczos Modes}
The linear coupling parameter $ {\mathbf g}_{22}$ in Eq.~\ref{eq:locaiHam2} defines
a force
along a vector connecting
the initial and final equilibrium geometries of the molecule.
This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
using the ER localization
scheme to approximate the donor and acceptor states.
By analyzing this force we can gain the insight into the dynamics of the transition as well as
open an avenue for developing improved approximations for transition rates.
In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
out a series of nuclear displacements that are most important for
the transition.   We refer to the highest-ranked mode identified by the algorithm
as the ``primary Lanczos mode'' (PLM).
The process of finding the PLMs is initiated by defining the vector ${\mathbf v}_{1} = {\mathbf g}_{22}$.
At each step indexed by $k$,  we define a projection operator
\begin{eqnarray}
{\mathbf P}_{k} = {\mathbf v}_{k}\otimes  {\mathbf v}_{k}
\end{eqnarray}
and its complement ${\mathbf Q}_{k} = {\mathbf I}  - {\mathbf P}_{k}$.
We also construct
\begin{eqnarray}
\mathbf p = \sum_{k} \mathbf P_{k}
\end{eqnarray}
as  the total projection operator for all ${k} \le N$ modes.
We then project the hessian matrix $\mathbf\Omega$ into each subspace {\em viz.}
\begin{eqnarray}
\mathbf\Omega_{p} = \mathbf P_{k}\cdot \mathbf\Omega \cdot \mathbf P_{k} \,\, \& \,\, \mathbf\Omega_{q} = \mathbf Q_{k}\cdot \mathbf\Omega \cdot  \mathbf Q_{k}
\end{eqnarray}
and diagonalize each to obtain eigenvalues and eigenvectors $\{\alpha_{p}, {\mathbf M}_{p}\}$ and $\{\alpha_{q}, {\mathbf M}_{q}\}$
respectively.  $\mathbf\Omega_{p} $ and $\mathbf\Omega_{q}$ are $N\times N$ matrices.
The first set of these  will have a single
non-trivial eigenvalue and the second set
will have $N-k$ non-trivial eigenvalues. We then collect the non-trivial eigenvectors associated with each
to form the orthogonal transformation matrix
\begin{eqnarray}
{\mathbf M}_{k} = \{{\mathbf M}_{p},{\mathbf M}_{q}\}.
\end{eqnarray}
and again transform the full hessian $\mathbf\Omega$ into this new vector space to form the $N\times N$ matrix $\mathbf\Omega'$.
 At each step in the iteration, the transformed hessian, $\mathbf\Omega'$ is in the form of a
$k\times k$ tri-diagonal submatrix in the upper-left part of the matrix and
a diagonal submatrix in the lower-right.

>>>>

\chapter{Primary Mode and Its Relation to Transfer Dynamics}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, Computing Intramolecular Charge and Energy Transfer Rates Using Optimal Modes. The Journal of Chemical Physics \textbf{142}, 244114 (2015)}\label{chap:chapt3}

@@

% One of the most important and fundamental processes in chemical  dynamics is
% that of energy and charge transfer between molecular species.  The mechanism
% itself is highly quantum mechanical in nature and involves strong coupling between nuclear and
% electronic degrees of freedom.  The seminal model for the calculation of the transfer rate for this process
% was developed by Marcus in the 1950s \cite{marcus1956theory,marcus1965theory,marcus1993electron}
% \begin{equation}
% k_{Marcus}=\frac{2\pi}{\hbar}|V_{ab}|^{2}\frac{1}{\sqrt{4\text{\ensuremath{\pi}}k_{B}T\lambda}}e^{-(\lambda+ \Delta G^{o})^{2}/4\text{\ensuremath{\lambda}}k_{B}T},
% \end{equation}
% which relates the Fermi golden-rule transition rate, $k_{Marcus}$
% to the thermodynamic driving force $\Delta G^{o}$ and the reorganization energy $\lambda$.
% One of the most striking predictions of this theory is that as the free energy difference between the final and initial state increases, the transition rate reaches its maximum,
% and further increases in the energy off-set leads to slower transition rates.
% This ``inverted regime''  was confirmed by Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
% nearly 30 yrs later.

% Numerous improvements to the Marcus model have been presented over the years and
% a detailed exploration of each is well beyond the scope of this work.
% Aside from the electronic coupling, $V_{ab}$,  the other terms in the expression of rate constant arise from
% a semi-classical approximation to the overlap between the initial vibrational states of the donor and the
% the final  states of the acceptor state. It suffices to say that most of the
% efforts focus upon incorporating more molecular-level detail into the couplings and vibrational modes
% used in computing these terms.

% A number of years ago,  we developed a time-convolutionless  master equation approach (TCLME) for computing
% state-to-state rate in which the coupling between  states depends upon the
% nuclear coordinates \cite{pereverzev2006time}. This approach incorporates a fully quantum
% mechanical treatment of both the nuclear and electronic degrees of freedom and recovers
% the Marcus rate equation in the semi-classical limit.  The model itself is parameterized by the
% vibrational normal mode frequencies, the electronic energies, and energy derivatives
% at a reference configuration obtained from {\em ab initio} quantum  chemistry computations.
% The approach has been intensively used and testified by our group to compute state-to-state
% transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
%  \cite{tamura2008phonon,tamura2007exciton,singh2009fluorescence,bittner2014noise}.
% Central to our work here is the use of a mode-projection scheme
%  % which is similar to the Page-rank algorithm used by internet search engines such as
%  % Google and Netflix\cite{brin1998anatomy, page2004method},
%  which parses out a
% reduced set of nuclear motions primarily coupled to the quantum transition.
% We refer to the modes identified early in the iterative process as the ``primary Lanczos modes'' or PLMs.

% Using the TCLME approach,  we recently investigated
% triplet-triplet excitation energy transfer between a naphthalene donor and a
% benzaldehyde acceptor linked by a variety of bridging units as shown in Fig.~\ref{struct}. \cite{yang2014intramolecular}
% \begin{figure}
% %\includegraphics[width=\columnwidth]{Chapters/chap3/D-B-A-Numbered.pdf}
% \includegraphics[width=\columnwidth]{Chapters/chap3/molecule1.pdf}
% \caption{Molecular structure of naphthalene donor and a
% benzaldehyde acceptor linked by various bridging units. }\label{struct}
% \end{figure}
% Such systems were the basis of a  classic series of experiments by
% Closs and Miller \cite{miller1984intramolecular,closs1988determination,closs1989connection}
% which verified the existence of the Marcus inverted regime.
% In Ref. \cite{yang2014intramolecular} we showed that both
% the autocorrelation function of the electronic coupling operators
% and the total transfer rate constant calculated using TCLME approach with only PLMs provide an
% excellent approximation to the exact correlation functions and rate
% constants computed using all normal modes, as well as to the experimental
% and recent theoretical values for the transfer rates \cite{subotnik2010predicting}.

In this chapter we analyze the symmetry of PLMs (see Fig. \ref{LanczosModes_chap2}) in model donor-bridge-acceptor systems as projected onto the local
 vibrational modes of the  donor (benzaldehyde)    and  acceptor (naphthalene) moieties.    By constructing the local modes
from the dominant normal modes in the projection,  one can deduce a relation between the PLMs,
fragment modes,  and normal modes for the entire molecule.
% The structure of this paper is as follows. We begin by reviewing the TCLME approach and how one generates the PLMs.
% Below we discuss the symmetry  of PLMs and their relation to a linear coordinate linking the initial/donor geometry to the final/acceptor geometry of the molecule.
%---NEED CONCLUDING STATEMENT----

% \section{Theoretical Model}

@@

% \subsection{Hamiltonian and Parameterization}

% We start with the  generic form for the diabatic Hamiltonian, describing two electronic states coupled with $N$ normal modes:
% \begin{eqnarray}
% H_{dia}=\left(\begin{array}{cc}
% \epsilon_{1} & V_{12}\\
% V_{21} & \epsilon_{2}
% \end{array}\right)
% +\left(\begin{array}{cc}
% {\mathbf g}_{11}&{\mathbf g}_{12} \\
% {\mathbf g}_{21} &{\mathbf g}_{22}
% \end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}.
% \nonumber \\
% \end{eqnarray}
% Here, the first term contains the electronic energies, $\epsilon_{1}$ and $\epsilon_{2}$ computed at a
% reference geometry--typically that of the donor or acceptor state. $V_{ij}$ is the diabatic coupling between them.  The second term represents the
% linear coupling between the electronic and nuclear degrees of freedom given in terms of the mass-weighted
% normal coordinates $\mathbf q$.   The diagonal terms
% give the diabatic displacement forces between the reference geometry and the two states.
% The remaining two terms correspond to the harmonic motions of the nuclear normal modes, given here in mass-weighted normal coordinates.
% In the normal mode basis, $\mathbf \Omega$  is diagonal with elements corresponding to the normal mode frequencies, $\omega_{j}^{2}$.

% If we choose one of the states as the reference state, then either $\mathbf g_{11}$ or $\mathbf g_{22}$ will vanish. We further assume Condon approximation to neglect $\mathbf g_{12}$ and $\mathbf g_{21}$. Now the Hamiltonian is simplified to
% \begin{eqnarray}
% H_{dia}=\left(\begin{array}{cc}
% \epsilon_{1} & V_{12}\\
% V_{21} & \epsilon_{2}
% \end{array}\right)+\left(\begin{array}{cc}
% 0 & 0\\
% 0 & 1
% \end{array}\right) {\mathbf g}_{22}\cdot{\mathbf q}+H_{osc},
% \end{eqnarray}
% \label{eq:diaHam}
% where $H_{osc}$ is the harmonic oscillator Hamiltonian for the vibrational normal modes.

% To calculate transition rate, we transform to adiabatic representation. It is done via Edmiston-Ruendenberg (ER) localization \cite{subotnik2010predicting} implemented in Q-Chem and the electronic Hamiltonians
% on adiabatic and diabatic basis are related by the mixing angle $\theta$.
% \begin{equation}
% H_{dia,e}=\left(\begin{array}{cc}
% \cos\theta & -\sin\theta\\
% \sin\theta & \cos\theta
% \end{array}\right)\left(\begin{array}{cc}
% \epsilon_{1}  & 0 \\
% 0  & \epsilon_{2}
% \end{array}\right)\left(\begin{array}{cc}
% \cos\theta & \sin\theta\\
% -\sin\theta & \cos\theta
% \end{array}\right).
% \end{equation}
% The diabatic coupling is then given by
% \begin{eqnarray}
% V_{12}=\frac{1}{2}\sin2\theta\left(\epsilon_{2}-\epsilon_{1}\right).
% \end{eqnarray}
% The full adiabatic Hamiltonian reads:
% \begin{eqnarray}
% H&=&U^{T}H_{dia}U\nonumber  \\
% &=&\left(\begin{array}{cc}
% E_{1}  & 0 \\
% 0 & E_{2}
% \end{array}\right)+\left(\begin{array}{cc}
% \sin^{2}\theta & \frac{1}{2}\sin2\theta\\
% \frac{1}{2}\sin2\theta & \cos^{2}\theta
% \end{array}\right) {\mathbf g}_{22}.{\mathbf q} \nonumber \\
% &+& H_{osc}.\label{eq:locaiHam2}
% \end{eqnarray}
% where the electronic part is in the adiabatic basis with eigenenergies of $E_1$ and $E_2$ at certain reference geometry. The nuclear normal modes are described by $H_{osc}$ whereas $\theta$ is the mixing angle between two states.
% %to describe the coupling between two electronic states, $|1\rangle$ and $|2\rangle$  by a set of nuclear vibrational motionsdescribed by $H_{osc}$.  The angle $\theta$ gives the mixing angle between diabatic states and $E_1$ and $E_{2}$ are electronic energies computed at the same reference configuration.

% To parametrize our Hamiltonian, we assume the diabatic
% are a good approximation to the actual adiabatic potentials.
% This allows us to
% use the gradients of the adiabatic potentials to approximate the diabatic potentials.
% This approximation is  valid when the adiabatic (and diabatic) energy minima
% are far enough away from the crossing points and the mixing angles between the diabatic  and adiabatic
% states is small.
% Thus, all parameters in Eq.~\ref{eq:locaiHam2}  can be  obtained from
% standard  quantum chemical computations.
% As in our previous work, we use the Q-Chem 4.0 package  to obtain the vertical energies
%  from single point CI(S) calculations with 6-31G** basis set at a given
% reference geometry.   We then project the energy gradients onto the vibrational normal
% coordinates

% Our group has shown that the dynamics of Hamiltonian in the form of Eq.~\ref{eq:locaiHam2} can be expressed in a time-convolutionless mater equation \cite{pereverzev2006time}. The derivation is lengthy so we present it briefly.

% \subsection{Transition Rate and Autocorrelation}
% We start from a more general Hamiltonian:
% \begin{eqnarray}
% H=\left(\begin{array}{cc}
% \epsilon_{1} & 0\\
% 0 & \epsilon_{2}
% \end{array}\right)+\left(\begin{array}{cc}
% {\mathbf g}_{11}&{\mathbf g}_{12} \\
% {\mathbf g}_{21} &{\mathbf g}_{22}
% \end{array}\right)\cdot{\mathbf q} +\frac{{\mathbf p}^{2}}{2}+\frac{1}{2}\mathbf{q}^{T}\cdot\mathbf\Omega\cdot\mathbf{q}
% \nonumber \\
% % \label{ham1}
% \end{eqnarray}
% then perform a polaron transform
% using the unitary transformation \cite{grover1970exciton,rice1994excitons,pereverzev2006time}.
% \begin{eqnarray}
% U&=&e^{-\sum_{ni}\!\!\frac{g_{nni}}{\hbar\omega_i}|n\rangle \langle
% n|(a^{\dagger}_i-a_i)}
%  \nonumber \\
% &=&
% \sum_{n}|n\rangle \langle n|e^{-\sum_{i}\!\!\frac{g_{nni}}{\hbar\omega_i}(a^{\dagger}_i-a_i)}
% % \label{unitary}
% \end{eqnarray}
% under which the transformed Hamiltonian is written in terms of the
% diagonal elements
% \begin{eqnarray} \tilde H_0=U^{-1}H_0U
% =\sum_n\tilde\epsilon_n |n\rangle \langle
% n|+\sum_i\omega_ia^{\dagger}_ia_i,
%  \end{eqnarray}
% with  the renormalized electronic energies,
% \begin{eqnarray}
% \tilde\epsilon_n=\epsilon_n-\sum_{i}\frac{g_{nni}^2}{\hbar\omega_i},
% \end{eqnarray}
% and off-diagonal terms,
% \begin{eqnarray} \hat V_{nm}=\sum_{i}g_{nmi}\left(a^{\dagger}_i+
% a_i-\frac{2g_{nni}}{\hbar\omega_i}\right)e^{\sum_{j}\frac{(g_{nnj}-g_{mmj})}{\hbar\omega_j}(a^{\dagger}_j-a_j)}.
% % \label{opm}
% \end{eqnarray}
% % In the transformed (or dressed) picture the electronic transition from state
% % $|n\rangle$ to $|m\rangle$ is accompanied by the excitations of all the
% % normal phonon modes.  Transforming to the interaction representation
% % and performing a trace over the phonons gives the spectral density in
% % terms of the autocorrelation of the electron/phonon coupling
% % operators.
% % \begin{eqnarray}
% % S_{nm}(\tilde\omega) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}C_{nm}(t),\label{spec-dens}
% % \end{eqnarray}
% % where
% % $$
% %C_{nm}(t) = \int_{-\infty}^{\infty} dt e^{-i\tilde \omega t}\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle.\label{cor-fun}
% After lengthy derivation we get the autocorrelation function in the Heisenberg representation
% $$
% C_{nm}(t) =\langle \hat V_{nm}(t) \hat V_{mn}(0)\rangle,\label{cor-fun}
% $$
% where $\langle \cdots \rangle$ denotes a thermal average over the
% vibrational degrees of freedom.
% % The derivation and explicit form for the kernel in Eq.~\ref{spec-dens}  is quite lengthy and is given in
% % Ref.~\citenum{pereverzev2006time}.
% Using this approach , the golden-rule rates are given by
% \begin{eqnarray}
% k_{nm}=\lim_{\tau \to \infty}2{\rm Re}\int_{0}^{\tau}dt\left\langle \hat V_{nm}(0)\hat V_{mn}\left(t\right)\right\rangle e^{-i\tilde\omega_{nm}t}.
% % \label{gr-expression}
% \end{eqnarray}
% In a practical sense, we take $\tau$ to be some finite time at which the
% autocorrelation function $C(t)$
% has relaxed to zero.

% Later, we will use the $C_{nm}(t) $ to benchmark the convergence of our model with respect to
% the number of nuclear modes included in constructing the electronic coupling operator, $V_{nm}(t)$.
% For our purposes here,  an ``exact''  calculation involves including all nuclear vibrational modes.
% In our previous work we showed that both $C(t)$
% and the total transfer rate constant, $k_{nm}$ calculated using only the first few projected modes provide an
% excellent agreement with the exact quantities computed using  the full set of
% normal modes, as well as the experimental rates,
% when parameterized using accurate quantum chemical data \cite{yang2014intramolecular}.

% % Diagonalizing $H$ at a given nuclear configuration  provides the adiabatic potentials for our system, which can be used to approximate the diabatic potentials.

% % The linear coupling parameter $ {\mathbf g}_{22}$ defines
% % a force
% % along a vector connecting the
% % the initial and final equilibrium geometries of the molecule.
% % This vector, along with the diabatic mixing angle can be obtained from quantum chemistry
% % using the ER localization
% % scheme to approximate the donor and acceptor states.
% % By analyzing this force we can gain the insight into the dynamics of the transition as well as
% % open an avenue for developing improved approximations for transition rates.
% % In our previous work \cite{yang2014intramolecular},  we presented a Lanczos-base ranking algorithm that project
% % out a series of nuclear displacements that are most important for
% % the transition.   We refer to the highest-ranked mode identified by the algorithm
% % as the ``primary Lanczos mode'' (PLM).

% % \subsection{Computing spectral densities and transition rates}

% % Once a suitable set of parameters and vibrational modes  have been determined,
